Implicit yaddayadda

### 2011-10-26 papers/PLDI2012/implicitization.tex
petites modifs

Our analysis tool currently only operates over scalar variable and cannot directly cope with arrays or memory accessed through pointers. We therefore run it after the ``memory to registers'' (\texttt{mem2reg}) optimization phase in LLVM, which lifts most memory accesses to scalar variables.
The remaining memory accesses are treated as undefined values, as are the return values of function calls. For better precision, we also apply function inlining to the program.

@@

Table \ref{tab:time} gives the execution time of the different analysis
techniques. It is interesting to see that \emph{Guided Static Analysis} and
\emph{Path-focusing} technique are sometimes faster than the classical
algorithm. Our techniques are slower, but on the same order of magnitude than
the previous techniques.

>>>>

Our analysis tool currently only operates over scalar variable and cannot directly cope with arrays or memory accessed through pointers. We therefore run it after the ``memory to registers'' (\texttt{mem2reg}) optimization phase in LLVM, which lifts most memory accesses to scalar variables.
The remaining memory accesses are treated as undefined values, as are the return
values of function calls. For better precision, we apply function inlining
to the program, and we also unroll the loops once.

@@

Table \ref{tab:time} gives the execution time of the different analysis
techniques. It is interesting to see that \emph{Guided Static Analysis} and
\emph{Path-focusing} technique are sometimes faster than the classical
algorithm. Our techniques are slower, but on the same order of magnitude as
the previous techniques.
